How Slow do my Transient Typechecks Go?

### 2019-08-16 paper.tex
Some references for work on performance visualizations for parallel programming
Signed-off-by: Stefan Marr <git@stefan-marr.de>

@@

>>>>

The high-performance computing community also has been investigating how
tools and visualization can help developers to utilize their systems
more efficiently \citep{Papenhausen:2016:IVT,daSilva:2019:PSV}.
Their focus is typically on parallelisation opportunities,
guided by runtime feedback, cost models, or heuristics. 
The large body of work\citep{Isaacs:2014:PerfViz} uses various approaches,
though, we are not aware of work has used an approach as ours.
One may argue, this is largely a question of practicality.\sm{
i put this in to hint at issues with usability.}

@@

\sm{is our approach practical. Is it useful for day-to-day development?
What's its context, use, general application?}
